Software

### 2025-09-12 software.qmd
update software section

>>>>

## `mvBayes`
I'm a developer of the `mvBayes` R and and Python Package ([Github - R](https://github.com/sandialabs/mvBayesR);[Github - Python](https://github.com/sandialabs/mvBayesPy))

Implementation of the multivariate Bayesian regression (mvBayes) framework. Decomposes a multivariate/functional response using a user-specified orthogonal basis decomposition, and then models each basis component independently using an arbitrary user-specified (univariate) Bayesian regression model. Includes prediction and plotting methods.
